Supplementary Material

### 2025-05-29 draft/ms-adj-appendix.Rmd
revision

---
output:
  # bookdown::word_document2:
    # reference_docx: "word-template.docx"
  bookdown::pdf_document2:
    toc: yes
    keep_tex: true
    number_sections: yes
    pandoc_args: !expr rmdfiltr::add_wordcount_filter(rmdfiltr::add_citeproc_filter(args = NULL))
    #latex_engine: xelatex
always_allow_html: true
header-includes:
  #- \usepackage{setspace}\doublespace
  # - \usepackage[nolists, fighead, tabhead]{endfloat}
  # - \usepackage{endnotes}
  # - \let\footnote=\endnote
  # - \setlength{\headheight}{14.5pt}
  # - \setlength{\headheight}{13.6pt}
  # - \usepackage{fancyhdr}
  # - \pagestyle{fancy}
  # - \lhead{N.I. Hoffmann} 
  # - \rhead{`r format(Sys.time(), '%B %e, %Y')`}
  # - \counterwithin{figure}{section}
  # - \counterwithin{table}{section}

@@

@@

dml_sim <- function(dat, seed = 185){
  library(mlr3)
  library(mlr3learners)

@@

compare_tbl <- function(model_list, treatment){
  out_list <- list()
  k <- 1
  for(model_set in model_list){
    names(model_set[[2]]) <- c('estimate', 'std.error')

    out_list[[k]] <- tidy(model_set[[1]]) %>%
      filter(term == treatment) %>%
      bind_rows(bind_rows(model_set[[2]])) %>%
      bind_rows(model_set[[3]]) %>%
      mutate(term = c('Original', 'AIPW (GRF)', 'DML (SuperLearner)'), p.value = p_val(estimate, std.error))

@@

@@

  return(list(grf = grf_out, 
              dml = dml_out,
              dml_cre = dml_cre_out,
              dml_wg_cre = dml_wg_cre_out))
}
```

@@

# Tables of Results

```{r dorie-results-table}
sim_results %>%
  # bind_rows(mutate(aipw_df, method = as.factor('aipw (original)'))) %>%
  filter(set == 'main') %>%
  group_by(estimator, method) %>%
  summarize(bias = round(mean(ate - truth, na.rm = T), 3),
            # var = round(var(ate, na.rm = T), 3),
            percent_bias = bias/sd(ate, na.rm = T),
            rmse = round(sqrt(mean((ate - truth)^2, na.rm = T)), 3),
            mae = median(abs(ate - truth), na.rm = T),
            comp_time = median(comp_time),
            fail_count = n() - sum(!is.na(ate))
              ) %>%
  select(method, everything()) %>%
  arrange(method, estimator) %>% 
  # mutate(bias = as.character(bias),
  #        rmse = as.character(rmse)) %>%
  # mutate(across(bias:comp_time, function(x){as.character(round(x, 3))})) %>%
  kableExtra::kable(booktabs = T, 
                    digits = 3,
                    linesep = '',
                    caption = 'Main datasets: Results of Monte Carlo simulations using the first 20 datasets from Dorie et al. (2019), 10 replications each. Percent bias is calculated as the estimator\'s bias as a percentage of its standard error, rmse is root mean squared error, mae is median absolute error, and comp\\_time is median computation time measured in seconds for each dataset.') %>%
  kable_styling(latex_options = c("hold_position"))
```

@@

```{r dorie-linear-results}
sim_results %>%
  filter(set == 'linear') %>%
  # bind_rows(mutate(aipw_df, method = as.factor('aipw (original)'))) %>%
  group_by(estimator, method) %>%
  summarize(bias = round(mean(ate - truth, na.rm = T), 3),
            percent_bias = bias/sd(ate, na.rm = T),
            rmse = round(sqrt(mean((ate - truth)^2, na.rm = T)), 3),
            mae = median(abs(ate - truth), na.rm = T),
            comp_time = median(comp_time),
            fail_count = n() - sum(!is.na(ate))
              ) %>%
  select(method, everything()) %>%
  arrange(method, estimator) %>%
  # mutate(across(bias:comp_time, function(x){as.character(round(x, 3))})) %>%
  kableExtra::kable(booktabs = T, 
                    digits = 3,
                    linesep = '',
                    caption = 'Linear datasets: Results of Monte Carlo simulations using the two datasets from Dorie et al. (2019), with linear data generating processes, 100 replications each ("linear"). Percent bias is calculated as the estimator\'s bias as a percentage of its standard error, rmse is root mean squared error, mae is median absolute error, and comp\\_time is median computation time measured in seconds for each dataset.') %>%
  kable_styling(latex_options = c("hold_position"))
```

@@

```{r dorie-results-size}
sim_results %>%
  filter(set %in% c('small', 'large')) %>% 
  group_by(estimator, method, size) %>%
  summarize(bias = round(mean(ate - truth, na.rm = T), 3),
            percent_bias = bias/sd(ate, na.rm = T),
            rmse = round(sqrt(mean((ate - truth)^2, na.rm = T)), 3),
            mae = median(abs(ate - truth), na.rm = T),
            comp_time = median(comp_time),
            fail_count = n() - sum(!is.na(ate))
              ) %>%
  select(method, everything()) %>%
  arrange(method, estimator, size) %>%  
  # mutate(bias = as.character(bias),
  #        rmse = as.character(rmse)) %>%
  # mutate(across(bias:comp_time, function(x){as.character(round(x, 3))})) %>%
  kableExtra::kable(booktabs = T, 
                    digits = 3,
                    linesep = '',
                    longtable = T,
                    caption = 'Sample size: Results of Monte Carlo simulations using dataset 7 from Dorie et al. (2019) with varying sample sizes, 20 replications each. Percent bias is calculated as the estimator\'s bias as a percentage of its standard error, rmse is root mean squared error, mae is median absolute error, and comp\\_time is median computation time measured in seconds for each dataset.') %>%
  kable_styling(latex_options = c("hold_position")) #'repeat_header')) 
```

@@

# Replications with Fixed Effects

The tables below present estimates from the *ASR* replications discussed in the main text, but with the addition of two other models implementing methods proposed by @clarke_2024_double that incorporate individual or group fixed effects into DML. The authors' package, `XTDML`, builds on the `DoubleML` package. I use two of their procedures. First, correlated random effects (CRE) models explicitly model the correlation between the group-level components in both the treatment and outcome models. Second, the authors' "hybrid" model combines CRE with a within-group estimator that partials out group means from all variables, similar to the mechanics of fixed effects in OLS. I present results using fixed effects for each model, whether or not the original model uses fixed effects. The original models from @aksoy_2022_commitment use fixed effects throughout. @biegert_2023_they do not employ fixed effects in any of their original models. @nussio_2024_dark uses fixed effects in the fourth model in Tables 2 and 4 and in all models in Table 5.

```{r rep-aksoy}
readRDS(here('replication', 'aksoy_rep.RDS')) %>%
  huxtable::huxreg(statistics = NA,
                   note = '{stars}. Covariates include GDP growth, population, turnout, number of parliamentary seats in province in Model 2 and 3; Models 3 also adjusts for the lagged value of the dependent variable (i.e., one election lagged Islamic votes); cluster robust standard errors are in parentheses. The AIPW (GRF) model does not drop incomplete observations.') %>%
  huxtable::insert_row(c('Covariates', 'No', rep('Yes', 2)), after = nrow(.) - 1) %>%
  huxtable::insert_row(c('Lagged dependent variable', 'No', 'No', 'Yes'), after = nrow(.) - 1) %>%
  huxtable::insert_row(c('Election year fixed effects', 'Yes', 'Yes', 'Yes'), after = nrow(.) - 1) %>%
  huxtable::insert_row(c('Province fixed effects', 'Yes', 'Yes', 'Yes'), after = nrow(.) - 1) %>%
  huxtable::set_top_border((nrow(.)-4):(nrow(.)-1), value = 0) %>%
  huxtable::set_top_border((nrow(.)-4), 2:4) %>%
  huxtable::set_caption('Replication of Aksoy et al. (2022) Table 2, models for outcome of Islamic Votes: "Effect of Fasting Hours (Daylength) during Ramadan on Various Outcome Variables Based on Regression Models That Include Fixed Effects for Provinces and Election Years"') %>%
  huxtable::set_width(.8) %>%
  huxtable::set_all_padding(0) %>%
  huxtable::set_latex_float('h!')

# read_rds(here('replication', 'aksoy_tab.RDS')) %>%
#   huxtable::as_flextable() %>%
#   flextable::hline(7:8, 1:4, border = officer::fp_border(width = 0)) %>%
#   flextable::hline(7, 2:4) %>%
#   flextable::hline(9) %>%
#   flextable::set_caption('Replication of Aksoy et al. (2022) Table 2, models for outcome of Islamic Votes: "Effect of Fasting Hours (Daylength) during Ramadan on Various Outcome Variables Based on Regression Models That Include Fixed Effects for Provinces and Election Years"')
```

@@

```{r rep-biegert}
readRDS(here('replication', 'biegert_rep.RDS')) %>%
  huxtable::huxreg(statistics = NA,
                   note = '{stars}. With no control variables, Model 1 could not be estimated using DML with a SuperLearner. Model 2 adjusts for year (fixed effects in original model), height (cm), position, age at league entry, being Black, and NBA tenure. Model 3 adds controls for the previous year\'s average points per 36 minutes, average assists per 36 minutes, average rebounds per 36 minutes, minutes played, whether the team reached playoffs, the team\'s win percentage, and whether it was a big market team. Model 4 adds controls for current average points, average assists, and average rebounds per 36 minutes. Model 5 additionally controls for current minutes played, whether the team reaches the playoffs, the team win percentage, and whether it is a big market team. Player clustered standard errors are in parentheses. None of the original models includes player fixed effects. The AIPW (GRF) model does not drop incomplete observations.') %>%
  huxtable::insert_row(c('Baseline confounders', 'No', rep('Yes', 4)), after = nrow(.) - 1) %>%
  huxtable::insert_row(c('Prior situation + performance', rep('No', 2), rep('Yes', 3)), after = nrow(.) - 1) %>%
  huxtable::insert_row(c('Current performance', rep('No', 3), rep('Yes', 2)), after = nrow(.) - 1) %>%
  huxtable::insert_row(c('Current situation', rep('No', 4), rep('Yes', 1)), after = nrow(.) - 1) %>%
  # huxtable::insert_row(c('Cumul. AS + cumul. mediators', rep('No', 5), 'Yes'), after = nrow(.) - 1) %>%
  huxtable::set_top_border((nrow(.)-4):(nrow(.)-1), value = 0) %>%
  huxtable::set_top_border((nrow(.)-4), 2:6) %>%
  huxtable::set_caption('Replication of Biegert et al. (2023) Table 3: "Average Marginal Effects from Logistic Regression Models of All-Star Nomination"') %>%
  huxtable::set_width(1) %>%
  huxtable::set_all_padding(0) %>%
  huxtable::set_latex_float('h!')

# read_rds(here('replication', 'biegert_tab.RDS')) %>%
#   huxtable::as_flextable() %>%
#   flextable::hline(7:11, 1:7, border = officer::fp_border(width = 0)) %>%
#   flextable::hline(7, 2:7) %>%
#   flextable::padding(padding = 0, part = "all") %>% 
#   flextable::autofit() %>%
#   flextable::hline(12) %>%
#   flextable::set_caption('Replication of Biegert et al. (2023) Table 3: "Average Marginal Effects from Logistic Regression Models of All-Star Nomination"')
```

```{r rep-nussio-ind}
readRDS(here('replication', 'nussio_ind_rep.RDS')) %>%
  huxtable::huxreg(statistics = NA,
                   note = "{stars}. Data come from a representative survey of residents of Mexico City conducted in February 2022. Models estimate the effect of the log number of names that respondents know in their colonia (neighborhood) on whether they had ever participate in a lynching. Model 1 controls for the extent to which people trust others living in their neighborhood. Model 2 adds controls for education, age, female, number of light bulbs, and unemployment. Model 3 additionally controls for employment, being Catholic or non-religious, whether someone has participated in a fight, whether parents live in the colonia, trust in government, garbage on the street, and residential street block. Colonia clustered standard errors are in parentheses. Model 4 adds colonia fixed effects. The AIPW (GRF) model does not drop incomplete observations.") %>%
  huxtable::insert_row(c('Colonia FE', 'No', 'No', 'No', 'Yes'), after = nrow(.) - 1) %>%
  huxtable::insert_row(c('Control variables', 'No', 'Some', 'All', 'All'), after = nrow(.) - 1) %>%
  huxtable::set_top_border((nrow(.)-2):(nrow(.)-1), value = 0) %>%
  huxtable::set_top_border((nrow(.)-2), 2:5) %>%
  huxtable::set_caption('Replication of Nussio (2024) Table 2: "Individual-Level Analysis: Community Ties and Lynching Participation"') %>%
  huxtable::set_width(.8) %>%
  huxtable::set_all_padding(0) %>%
  huxtable::set_latex_float('h!')

# read_rds(here('replication', 'nussio_ind_tab.RDS')) %>%
#   huxtable::as_flextable() %>%
#   flextable::hline(7:8, 1:5, border = officer::fp_border(width = 0)) %>%
#   flextable::hline(7, 2:5) %>%
#   flextable::hline(9) %>%
#   flextable::set_caption('Replication of Nussio (2024) Table 2: "Individual-Level Analysis: Community Ties and Lynching Participation"')
```

```{r rep-nussio-ag}
readRDS(here('replication', 'nussio_ag_rep.RDS')) %>%
  huxtable::huxreg(statistics = NA,
                   note = "{stars}. Models estimate the effect of neighborly cooperation -- operationalized by the proportion of respondents who think that most neighbors help each other in problems related to electric lighting -- on the log municipal lynching rate. Model 1 adds controls for the proportion of respondents in a municipality that trust their neighbors. Model controls for population, area in square kilometers, poverty rate, Gini coefficient, share indigenous people, non-religious population, homicide rate, and robbery rate. Model 3 adds controls for household victimization and trust in army. Model 4 adds estado (state) fixed effects. Municipality clustered standard errors are in paratheses. The AIPW (GRF) model does not drop incomplete observations.") %>%
  huxtable::insert_row(c('Control variables', 'No', 'Some', 'All', 'All'), after = nrow(.) - 1) %>%
  huxtable::insert_row(c('Estado FE', 'No', 'No', 'No', 'Yes'), after = nrow(.) - 1) %>%
  huxtable::insert_row(c('Estado clustered SE', 'Yes', 'Yes', 'Yes', 'No'), after = nrow(.) - 1) %>%
  huxtable::set_top_border((nrow(.)-3):(nrow(.)-1), value = 0) %>%
  huxtable::set_top_border((nrow(.)-3), 2:5) %>%
  huxtable::set_caption('Replication of Nussio (2024) Table 4: "Aggregate-Level Analysis: Community Ties and Lynching Rate"') %>%
  huxtable::set_width(.8) %>%
  huxtable::set_all_padding(0) %>%
  huxtable::set_latex_float('h!')

# read_rds(here('replication', 'nussio_ag_tab.RDS')) %>%
#   huxtable::as_flextable() %>%
#   flextable::hline(7:9, 1:5, border = officer::fp_border(width = 0)) %>%
#   flextable::hline(7, 2:5) %>%
#   flextable::hline(10) %>%
#   flextable::set_caption('Replication of Nussio (2024) Table 4: "Aggregate-Level Analysis: Community Ties and Lynching Rate"')
```

>>>>

---
output:
  # bookdown::word_document2:
    # reference_docx: "word-template.docx"
  bookdown::pdf_document2:
    toc: yes
    keep_tex: true
    number_sections: yes
    pandoc_args: !expr rmdfiltr::add_wordcount_filter(rmdfiltr::add_citeproc_filter(args = NULL))
    #latex_engine: xelatex
always_allow_html: true
header-includes:
  - \usepackage{caption}
  #- \usepackage{setspace}\doublespace
  # - \usepackage[nolists, fighead, tabhead]{endfloat}
  # - \usepackage{endnotes}
  # - \let\footnote=\endnote
  # - \setlength{\headheight}{14.5pt}
  # - \setlength{\headheight}{13.6pt}
  # - \usepackage{fancyhdr}
  # - \pagestyle{fancy}
  # - \lhead{N.I. Hoffmann} 
  # - \rhead{`r format(Sys.time(), '%B %e, %Y')`}
  # - \counterwithin{figure}{section}
  # - \counterwithin{table}{section}

@@

lm_lin_continuous <- function (formula, covariates, data, weights, subset, clusters, 
  se_type = NULL, ci = TRUE, alpha = 0.05, return_vcov = TRUE, 
  try_cholesky = FALSE) 
{
  if (length(all.vars(f_rhs(formula))) > 1) {
    stop("The `formula` argument, `", format(formula), "`, must only have the ", 
      "treatment variable on the right-hand side of the formula. Covariates ", 
      "should be specified in the `covariates` argument like so:\n`covariates = ", 
      paste0("~ ", paste(all.vars(f_rhs(formula))[-1], 
        sep = " + ")), "`.", "\n\n See ?lm_lin.")
  if (!inherits(covariates, "formula")) {
    stop("The `covariates` argument must be specified as a formula:\n", 
      "You passed an object of class ", class(covariates))
  cov_terms <- terms(covariates)
  if (attr(cov_terms, "response") != 0) {
    stop("Must not specify a response variable in `covariates`` formula.\n", 
      "`covariates` must be a right-sided formula, such as '~ x1 + x2 + x3'")
  if (length(attr(cov_terms, "order")) == 0) {
    stop("`covariates` must have a variable on the right-hand side, not 0 or 1")
  full_formula <- update(formula, reformulate(c(".", labels(cov_terms))))
  datargs <- enquos(formula = full_formula, weights = weights, 
    subset = subset, cluster = clusters)
  data <- enquo(data)
  model_data <- clean_model_data(data = data, datargs)
  outcome <- as.matrix(model_data$outcome)
  n <- nrow(outcome)
  design_matrix <- model_data$design_matrix
  weights <- model_data$weights
  cluster <- model_data$cluster
  has_intercept <- attr(terms(formula), "intercept")
  treat_col <- which(attr(design_matrix, "assign") == 1)
  treatment <- design_matrix[, treat_col, drop = FALSE]
  design_mat_treatment <- colnames(design_matrix)[treat_col]
  # if (any(!(treatment %in% c(0, 1)))) {
  #   vals <- sort(unique(treatment))
  #   if (has_intercept) 
  #     vals <- vals[-1]
  #   n_treats <- length(vals)
  #   names(vals) <- paste0(colnames(design_matrix)[treat_col], 
  #     vals)
  #   treatment <- outer(drop(treatment), vals, function(x, 
  #     y) as.numeric(x == y))
  # }
  demeaned_covars <- design_matrix[, setdiff(colnames(design_matrix), 
    c(design_mat_treatment, "(Intercept)")), drop = FALSE]
  if (is.numeric(weights)) {
    center <- apply(demeaned_covars, 2, weighted.mean, weights)
  else {
    center <- colMeans(demeaned_covars)
  demeaned_covars <- sweep(demeaned_covars, 2, center)
  original_covar_names <- colnames(demeaned_covars)
  colnames(demeaned_covars) <- paste0(ifelse(grepl("\\:|(^.+\\()", 
    colnames(demeaned_covars)), paste0("(", colnames(demeaned_covars), 
    ")"), colnames(demeaned_covars)), "_c")
  n_treat_cols <- ncol(treatment)
  n_covars <- ncol(demeaned_covars)
  n_int_covar_cols <- n_covars * (n_treat_cols)
  interacted_covars <- matrix(0, nrow = n, ncol = n_int_covar_cols)
  interacted_covars_names <- character(n_int_covar_cols)
  for (i in 1:n_covars) {
    covar_name <- colnames(demeaned_covars)[i]
    cols <- (i - 1) * n_treat_cols + (1:n_treat_cols)
    interacted_covars[, cols] <- treatment * demeaned_covars[, 
      i]
    interacted_covars_names[cols] <- paste0(colnames(treatment), 
      ":", covar_name)
  colnames(interacted_covars) <- interacted_covars_names
  if (has_intercept) {
    X <- cbind(matrix(1, nrow = n, ncol = 1, dimnames = list(NULL, 
      "(Intercept)")), treatment, demeaned_covars, interacted_covars)
  else {
    if (n_treat_cols == 1) {
      X <- cbind(treatment, demeaned_covars, interacted_covars)
    else {
      X <- cbind(treatment, interacted_covars)
  return_list <- lm_robust_fit(y = outcome, X = X, weights = weights, 
    cluster = cluster, ci = ci, se_type = se_type, alpha = alpha, 
    return_vcov = return_vcov, try_cholesky = try_cholesky, 
    has_int = has_intercept, iv_stage = list(0))
  return_list <- lm_return(return_list, model_data = model_data, 
    formula = formula)
  return_list[["scaled_center"]] <- center
  setNames(return_list[["scaled_center"]], original_covar_names)
  return_list[["call"]] <- match.call()
  return(return_list)

environment(lm_lin_continuous) <- asNamespace('estimatr')
assignInNamespace("lm_lin", lm_lin_continuous, ns = "estimatr")

@@

dml_sim <- function(dat, seed = 185){

@@

p_val <- function(estimate, std.error){
  z <- estimate / std.error
  2*(1 - pnorm(abs(as.numeric(z))))
}

compare_tbl <- function(model_list, treatment, tidy = T){
  out_list <- list()
  k <- 1
  for(model_set in model_list){
    names(model_set$grf) <- c('estimate', 'std.error')

    if(tidy == T){
    original_model <- tidy(model_set$original) %>%
      filter(term == treatment)
    } else{
      original_model <- model_set$original
    }

    out_list[[k]] <- original_model %>%
      bind_rows(bind_rows(model_set$grf)) %>%
      bind_rows(model_set$dml) %>%
      bind_rows(model_set$dml_cre) %>%
      bind_rows(model_set$dml_wg_cre) %>%
      mutate(term = c('Original', 'AIPW (GRF)', 'DML (SuperLearner)', 
                      'DML (SuperLearner), CRE FE', 'DML (SuperLearner), hybrid FE'), 
             p.value = p_val(estimate, std.error)) %>%
      remove_rownames() %>%
      tibble()

@@

# compare_tbl_notidy <- function(model_list){
#   out_list <- list()
#   k <- 1
#   for(model_set in model_list){
#     names(model_set[[2]]) <- c('estimate', 'std.error')
#     
#     
#     out_list[[k]] <- model_set[[1]] %>%
#       bind_rows(bind_rows(model_set[[2]])) %>%
#       bind_rows(model_set[[3]]) %>%
#       mutate(term = c('Original', 'AIPW (GRF)', 'DML (SuperLearner)'), p.value = p_val(estimate, std.error)) %>%
#       tibble()
#     
#     k <- k+1
#   }
#   return(out_list)
# }

@@

  return(list(grf = grf_out, 
              dml = dml_out,
              dml_cre = dml_cre_out,
              dml_wg_cre = dml_wg_cre_out))
}

@@

# Main Simulations

```{r dorie-results-table}
sim_results %>%
  # bind_rows(mutate(aipw_df, method = as.factor('aipw (original)'))) %>%
  filter(set == 'main') %>%
  group_by(estimator, method) %>%
  summarize(bias = round(mean(ate - truth, na.rm = T), 3),
            # var = round(var(ate, na.rm = T), 3),
            percent_bias = bias/sd(ate, na.rm = T),
            rmse = round(sqrt(mean((ate - truth)^2, na.rm = T)), 3),
            mae = median(abs(ate - truth), na.rm = T),
            comp_time = median(comp_time),
            fail_count = n() - sum(!is.na(ate))
              ) %>%
  select(method, everything()) %>%
  arrange(method, estimator) %>% 
  # mutate(bias = as.character(bias),
  #        rmse = as.character(rmse)) %>%
  # mutate(across(bias:comp_time, function(x){as.character(round(x, 3))})) %>%
  kableExtra::kable(booktabs = T, 
                    digits = 3,
                    linesep = '',
                    caption = 'Main datasets: Results of Monte Carlo simulations using the first 20 DGPs from Dorie et al. (2019), 10 replications each. Percent bias is calculated as the estimator\'s bias as a percentage of its standard error, rmse is root mean squared error, mae is median absolute error, and comp\\_time is median computation time measured in seconds for each dataset.') %>%
  kable_styling(latex_options = c("hold_position"))
```

@@

# Linear Simulations

```{r dorie-linear-results}
sim_results %>%
  filter(set == 'linear') %>%
  # bind_rows(mutate(aipw_df, method = as.factor('aipw (original)'))) %>%
  group_by(estimator, method) %>%
  summarize(bias = round(mean(ate - truth, na.rm = T), 3),
            percent_bias = bias/sd(ate, na.rm = T),
            rmse = round(sqrt(mean((ate - truth)^2, na.rm = T)), 3),
            mae = median(abs(ate - truth), na.rm = T),
            comp_time = median(comp_time),
            fail_count = n() - sum(!is.na(ate))
              ) %>%
  select(method, everything()) %>%
  arrange(method, estimator) %>%
  # mutate(across(bias:comp_time, function(x){as.character(round(x, 3))})) %>%
  kableExtra::kable(booktabs = T, 
                    digits = 3,
                    linesep = '',
                    caption = 'Linear DGPs: Results of Monte Carlo simulations using the two datasets from Dorie et al. (2019), with linear data generating processes, 100 replications each. Percent bias is calculated as the estimator\'s bias as a percentage of its standard error, rmse is root mean squared error, mae is median absolute error, and comp\\_time is median computation time measured in seconds for each dataset.') %>%
  kable_styling(latex_options = c("hold_position"))
```

@@

# Data Generating Processes

```{r dgp}
dgp_names <- c('Treat. assign.', 'Prob. of treat.',
               'Overlap', 'Response surface',
               'Alignment',
               'Treat. heterogeneity')

rename_vec <- names(aciccomp2016::parameters_2016)
names(rename_vec) <- dgp_names

sim_results_dgp <- sim_results %>%
  filter(set == 'main') %>%
  # mutate(paramter_num = ceiling(dataset/10)) %>%
  left_join(mutate(aciccomp2016::parameters_2016, dorie_dataset = row_number())) %>%
  rename(rename_vec) %>%
  mutate(estimator = if_else(is.na(estimator), 'NA', estimator),
         method_estimator = str_replace(method_estimator, 'superlearner', 'superl.')) %>%
  mutate(method_estimator = factor(method_estimator, levels = unique({.$method_estimator})))

dgp_list <- list()

for(name in dgp_names){

  dgp_list[[name]] <- sim_results_dgp %>%
    group_by(!!sym(name), method_estimator) %>%
    summarize(bias = round(mean(ate - truth, na.rm = T), 3),
            percent_bias = bias/sd(ate, na.rm = T),
            rmse = round(sqrt(mean((ate - truth)^2, na.rm = T)), 3),
            mae = median(abs(ate - truth), na.rm = T),
            datasets = n_distinct(dataset)
              )  %>%
    ungroup() %>%
    mutate(`DGP parameter` = name,
          dgp_value = as.character(!!sym(name))) %>%
    select(-!!sym(name))

bind_rows(dgp_list) %>%
  select(`DGP parameter`, dgp_value, everything()) %>%
  arrange(`DGP parameter`, dgp_value, rmse) %>%  
  # mutate(bias = as.character(bias),
  #        rmse = as.character(rmse)) %>%
  # mutate(across(bias:comp_time, function(x){as.character(round(x, 3))})) %>%
  kableExtra::kable(booktabs = T, 
                    digits = 3,
                    linesep = '',
                    longtable = T,
                    caption = 'Data generating process: Within each DGP value, estimates are sorted from lowest to highest RMSE, based on Monte Carlo simulations using the first 20 DGPs from Dorie et al. (2019), 10 replications each. Percent bias is calculated as the estimator\'s bias as a percentage of its standard error, rmse is root mean squared error, mae is median absolute error, and datasets shows the number of distinct datasets in the simulations with each particular DGP parameter.') %>%
  kable_styling(latex_options = c("hold_position")) #'repeat_header'))

@@

# Sample Sizes

```{r dorie-results-size}
sim_results %>%
  filter(set %in% c('small', 'large')) %>% 
  group_by(estimator, method, size) %>%
  summarize(bias = round(mean(ate - truth, na.rm = T), 3),
            percent_bias = bias/sd(ate, na.rm = T),
            rmse = round(sqrt(mean((ate - truth)^2, na.rm = T)), 3),
            mae = median(abs(ate - truth), na.rm = T),
            comp_time = median(comp_time),
            fail_count = n() - sum(!is.na(ate))
              ) %>%
  select(method, everything()) %>%
  arrange(method, estimator, size) %>%  
  # mutate(bias = as.character(bias),
  #        rmse = as.character(rmse)) %>%
  # mutate(across(bias:comp_time, function(x){as.character(round(x, 3))})) %>%
  kableExtra::kable(booktabs = T, 
                    digits = 3,
                    linesep = '',
                    longtable = T,
                    caption = 'Sample size: Results of Monte Carlo simulations using DGP 7 from Dorie et al. (2019) with varying sample sizes, 20 replications each. Percent bias is calculated as the estimator\'s bias as a percentage of its standard error, rmse is root mean squared error, mae is median absolute error, and comp\\_time is median computation time measured in seconds for each dataset.') %>%
  kable_styling(latex_options = c("hold_position")) #'repeat_header')) 
```

@@

<!-- # Replications -->

<!-- ```{r aksoy, eval = F} -->
<!-- aksoy <- read_dta(here('replication', 'aksoy.dta')) %>% -->
<!--   mutate(cid_num = as.integer(factor(cid))) %>% -->
<!--   as_factor() -->

<!-- # first three models from table 2 -->

<!-- m1 <- lm(ISL ~ `_Y28` + `_Y32` + `_Y42` + `_Y46` + `_Y50` + `_Y54` + `_Y57` + `_Y62` +  -->
<!--      `_Y66` + `_Y70` + `_Y71` + dlen + cid, -->
<!--    data = filter(aksoy, electyr == T)) # %>% -->
<!--   # tidy() %>% -->
<!--   # filter(!str_detect(term, 'cid'), !str_detect(term, '_Y')) -->

<!-- m2 <- lm(ISL ~ `_Y28` + `_Y32` + `_Y42` + `_Y46` + `_Y50` + `_Y54` + `_Y57` + `_Y62` +  -->
<!--      `_Y66` + `_Y70` + `_Y71` + dlen + cid + gdp_g + t + m + pop, -->
<!--    data = aksoy)  -->
<!--   # tidy() %>% -->
<!--   # filter(!str_detect(term, 'cid'), !str_detect(term, '_Y')) -->

<!-- m3 <- lm(ISL ~ `_Y28` + `_Y32` + `_Y42` + `_Y46` + `_Y50` + `_Y54` + `_Y57` + `_Y62` +  -->
<!--      `_Y66` + `_Y70` + `_Y71` + dlen + cid + gdp_g + t + m + pop + l_ISL, -->
<!--    data = aksoy)  -->
<!--   # tidy() %>% -->
<!--   # filter(!str_detect(term, 'cid'), !str_detect(term, '_Y')) -->

<!-- # aksoy %>% -->
<!-- #   filter(electyr == T) %>% -->
<!-- #   mutate(across(c(`_Y28`, `_Y32`, `_Y42`, `_Y46`, `_Y50`, `_Y54`, `_Y57`,  -->
<!-- #                   `_Y62`, `_Y66`, `_Y70`, `_Y71`), ~ .x - mean(.x, na.rm = T))) %>% -->
<!-- #   estimatr::lm_robust(ISL ~ dlen*(`_Y28` + `_Y32` + `_Y42` + `_Y46` + `_Y50` +  -->
<!-- #                                     `_Y54` + `_Y57` + `_Y62` + `_Y66` + `_Y70` + `_Y71` + cid), -->
<!-- #    data = .) %>% -->
<!-- #   tidy() %>% -->
<!-- #   filter(term == 'dlen') -->
<!-- #  -->
<!-- #  -->
<!-- # m1_lin <- estimatr::lm_robust(ISL ~ dlen*(`_Y28` + `_Y32` + `_Y42` + `_Y46` + `_Y50` + `_Y54` + `_Y57` + `_Y62` + `_Y66` + `_Y70` + `_Y71`) + cid, -->
<!-- #    data = filter(aksoy, electyr == T)) %>% -->
<!-- #   tidy() %>% -->
<!-- #   filter(term == 'dlen') -->
<!-- #  -->
<!-- #  -->
<!-- # m1_lin <- lm_lin_continuous(ISL ~ dlen, -->
<!-- #                            covariates = ~ `_Y28` + `_Y32` + `_Y42` + `_Y46` + `_Y50` + `_Y54` + `_Y57` + `_Y62` + -->
<!-- #      `_Y66` + `_Y70` + `_Y71` + cid, -->
<!-- #    data = filter(aksoy, electyr == T)) %>% -->
<!-- #   tidy() %>% -->
<!-- #   filter(term == 'dlen') -->
<!-- #  -->
<!-- #  -->
<!-- # m2_lin <- lm_lin_continuous(ISL ~ dlen, -->
<!-- #                            covariates = ~ `_Y28` + `_Y32` + `_Y42` + `_Y46` + `_Y50` + `_Y54` + `_Y57` + `_Y62` + -->
<!-- #      `_Y66` + `_Y70` + `_Y71` + cid + gdp_g + t + m + pop, -->
<!-- #    data = aksoy) %>% -->
<!-- #   tidy() %>% -->
<!-- #   filter(term == 'dlen')  -->
<!-- #  -->
<!-- #  -->
<!-- # m3_lin <- lm_lin_continuous(ISL ~ dlen, -->
<!-- #                            covariates = ~ `_Y28` + `_Y32` + `_Y42` + `_Y46` + `_Y50` + `_Y54` + `_Y57` + `_Y62` + -->
<!-- #      `_Y66` + `_Y70` + `_Y71` + dlen + cid + gdp_g + t + m + pop + l_ISL, -->
<!-- #    data = aksoy) %>% -->
<!-- #   tidy() %>% -->
<!-- #   filter(term == 'dlen')  -->

<!-- # aksoy_drop_na_y <- filter(aksoy, !is.na(ISL)) -->

<!-- m1_grf_dml <- dml_grf(outcome = 'ISL',  -->
<!--         treatment = 'dlen',  -->
<!--         covariates = c('year'),  -->
<!--         clustervar = 'cid_num', -->
<!--         dataset = aksoy, -->
<!--         target = 'all') -->

<!-- m2_grf_dml <- dml_grf(outcome = 'ISL',  -->
<!--         treatment = 'dlen',  -->
<!--         covariates = c('year', 'gdp_g', 't', 'm', 'pop'),  -->
<!--         clustervar = 'cid_num', -->
<!--         dataset = aksoy, -->
<!--         target = 'all') -->

<!-- m3_grf_dml <- dml_grf(outcome = 'ISL',  -->
<!--         treatment = 'dlen',  -->
<!--         covariates = c('year', 'gdp_g', 't', 'm', 'pop', 'l_ISL'),  -->
<!--         clustervar = 'cid_num', -->
<!--         dataset = aksoy, -->
<!--         target = 'all') -->

<!-- m1 <- data.frame(estimate = 7.159, std.error = 2.539) -->
<!-- m2 <- data.frame(estimate = 7.349, std.error = 2.491) -->
<!-- m3 <- data.frame(estimate = 5.317, std.error = 1.855) -->

<!-- compare_tbl(list(append(list(original = m1), m1_grf_dml),  -->
<!--                                   append(list(original = m2), m2_grf_dml),  -->
<!--                                   append(list(original = m3), m3_grf_dml)), -->
<!--                              tidy = F) %>% -->
<!--   write_rds(here('replication', 'aksoy_rep.RDS')) -->
